Anxiety: a decision-theoretic perspective

### 2019-01-10 manuscript/manuscript.tex
first pass at images unified under single color scheme
first pass at longidutinal figure

\documentclass[11pt]{article} % For LaTeX2e
\usepackage{manuscript,palatino}
\usepackage{graphicx}
\usepackage{amsfonts,amsmath}
\usepackage{algorithm, algpseudocode}%

@@

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

@@

Alternately, an agent may choose optimally in the present but may be uncertain of
its choice control in the future. In such a case, we deviate from the optimal
policy in the future. We can adopt a different function. There are a number to
choose from (Garcia \& Fernandez, 2015). Here we adopt the beta-pessimism criterion
(Gaskett, 2003):

@@

\begin{figure}
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../figures/01_field.png}}%
  }
  \caption{\textbf{Open Field}}
  \par Oooh so pretty.
\end{figure}

@@

\begin{figure}
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../figures/02_cliff.png}}%
  }
  \caption{\textbf{Cliff Walking}}
  \par You better watch out YOU BETTER WATCH OUT
\end{figure}

Discuss similar observations in other tasks (Bach et al., 2014; Sheynin et al., 2015).

@@

Discuss Bach behavioral inhibition.

@@

@@

>>>>

\documentclass[11pt]{article} % For LaTeX2e
\usepackage{manuscript, palatino}
\usepackage{graphicx}
\usepackage{amsfonts, amsmath}
\usepackage{algorithm, algpseudocode}%

@@

@@

Alternately, an agent may choose optimally in the present but may be uncertain of
its choice control in the future. In such a case, we deviate from the optimal
policy in the future. We can adopt a different function. There are a number to
choose from \cite{Garcia2015}. Here we adopt the beta-pessimism criterion
\cite{Gaskett2003}:

@@

\begin{figure}
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../figures/01_field.png}}%
  }
  \caption{\textbf{Open Field}}
  \par Current parameters: Reward = 10, Shock = -10, gamma = 0.95.
\end{figure}

@@

1. Open with definition of avoidance. Follow \cite{Arnaudova2017} in definitions, i.e.
the basic idea that avoidance is the distancing of oneself from real or perceived
threat.
2. Describe cliff walking environment. Need to discuss that we are expanding
on the result originally described in \cite{Gaskett2003}.
3. With increasing pessimism, agent further distances self from cliff. Note that
this is the optimal policy under those set of beliefs about the world.
4. This can explain how avoidance is maintained. Even with luck and chance in the
the world, these sets of beliefs actually lead to and sustain these behavioral
policies.

In discussion of section, need to also mention other relevant findings. Specifically,
need to describe the approach-avoidance findings of Bach (2014, 2017) and the
complex task findings of Sheynin et al., 2015.

\begin{figure}
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../figures/02_cliff.png}}%
  }
  \caption{\textbf{Cliff Walking}}
  \par Cliff = -100, Cost = -1, gamma = 0.99
\end{figure}

@@

In the third section of the results, we discuss approach-avoidance conflict.
This covers tasks such as the balloon analog risk task (BART) and the flight
initiation distance task, which has been found to correlate with anxiety. The
hallmark of these sorts of tasks is the tradeoff between increased reward vs.
the possibility of an aversive outcome (e.g. balloon pop, predation). Discuss
previous findings, i.e. earlier leave times.

We can show that this is easily explained by our model. A lack of belief of
future control predicts exiting while things are still good. (We see this in
Figure 3). The optimal policy in these environments is an earlier leaving time.

This can also be used to explain behavioral inhibition \cite{bach2015, khemka2017}.
The idea is slightly different than what is advocated. The claim here is that
in anxious individuals, the Q-values should be closer together, and thus there
should be longer waiting time. This requires demonstrating that decisions are
not made in advance; only at the time of decision making. This is something
I think we will have to argue. (Need to double check the literature here.)

\begin{figure}
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../figures/03_fid.png}}%
  }
  \caption{\textbf{Flight Initiation Distance}}
  \par remember to add parameters
\end{figure}

@@

Basically reviewing the arguments of Huys here \cite{Huys2012, Lally2017}.
Need to get facts straight before going through all of this.

\begin{figure}
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../figures/04_tree.png}}%
  }
  \caption{\textbf{Decision Tree}}
  \par remember to add parameters
\end{figure}

@@

\begin{figure}
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../figures/05_choice.png}}%
  }
  \caption{\textbf{Free Choice Premium}}
  \par remember to add parameters
\end{figure}
